%\include{header}
%\begin{document}

\chapter{Appendix} \label{chap:Appendix}

\section{Fourier Transform}

In science, one of the most fundamental principles is the superposition
principle. The superposition principle tells us that for a linear system
composed of different functions is the sum of the responses that would have
been caused by the different functions individually. Green's function is
written as the
superposition of infinitely many impulse response functions, which then makes
the response a superposition of impulse responses. Fourier transforms are like
Green's function, but instead of using impulse response functions, it uses
sinusoids instead.

Think of sinusoids (sines and cosines) as being the fundamental building blocks
for functions. From these functions, we can write any other function as a
superposition of those two functions, whether they be periodic or not. This can
be represented with an infinite series, known as the Fourier series.

First, let's suppose that $f(t)$ is a periodic function with a period
$T$, so that
\begin{equation}
    f(t)=f(t+T)
\end{equation}
for all values of $t$ \cite{DanielSteck}. We can represent this as

\begin{equation}
    f(t) = a_0 + b_0 + 2\sum_{n=1}^{\infty} a_n \cos(n\omega
    t)+2\sum_{n=1}^{\infty}b_n\sin(n\omega t)
    \label{eq:fourierseries}
\end{equation}
where $\omega=2\pi\nu=\frac{2\pi}{T}$ is the angular frequency, and $\nu$ is the frequency.
We can define the complex Fourier coefficient as

\begin{equation}
    c_n \equiv a_n+ib_n
\end{equation}
which allows for Equation~\ref{eq:fourierseries} to be rewritten as

\begin{equation}
    f(t) = a_0 + b_0 +\sum_{n=1}^{\infty} a_n \left( e^{in\omega t} +
    e^{-in\omega t} \right) - i\sum_{n=1}^{\infty} b_n \left( e^{in\omega t} -
    e^{-in\omega t} \right)
\end{equation}
This can be simplified farther

\begin{equation}
    f(t) = \sum_{n=-\infty}^{\infty}a_ne^{-in\omega t} + i\sum_{n=-\infty}^{\infty}b_ne^{-in\omega t}
\end{equation}

Now, using the complex Fourier coefficient defined earlier, we can get the
complex Fourier series

\begin{equation}
    f(t)=\sum_{n=-\infty}^{\infty}c_ne^{-in\omega t}
\end{equation}

Now, these same harmonic functions can be used to build aperiodic functions. An
aperiodic function corresponds to $T\rightarrow \infty$, so we need a
continuous spectrum to represent an aperiodic function, since there is more
information in the function than the aperiodic case.

\begin{equation}
    f(t)=\sum_{n=-\infty}^{\infty}c_ne^{-in\omega t} \rightarrow
    f(t)=\frac{1}{2\pi}\int_{-\infty}^{\infty} \tilde{f}(\omega) e^{-i\omega t}~d\omega
\end{equation}
This is the inverse Fourier transform. To find the amplitudes, $c_n$, which are
also called the Fourier transform,

\begin{equation}
    c_n = \frac{1}{T}\int_0^Te^{in\omega t} f(t) dt \rightarrow
    \tilde{f}(\omega) =\int_{-\infty}^{\infty}f(t)e^{i\omega t}~dt
\end{equation}
In a more common notation,

\begin{equation}
    \mathfrak{F} =\int_{-\infty}^{\infty}f(t)e^{i\omega t}~dt
    \qquad
    \mathfrak{F}^{-1} =\int_{-\infty}^{\infty}f(\omega)e^{-i\omega t}~d\omega
\end{equation}
where $\mathfrak{F}$ is the Fourier transform of  $f(t)$ and
$\mathfrak{F}^{-1}$ is the inverse Fourier transform of $f(t)$.


%*=============================================================================================*

